```{r echo=FALSE}
knitr::opts_chunk$set(error=TRUE)
options(digits=3)
## See tests/convertColor.R for details
library(grDevices0)
## library(grDevices)   ## if you have r-devel > r75340
```

# Summary of Known Behavior Changes

This is a summary of the know behavior changes between
`grDevices::convertColor@r75340` and that of the same function after applying
either the level-1 (`grDevices1::`) or level-2 patch (`grDevices2::`).  Unless
explicitly stated changes happen both with the level-1 and level-2 patches.

## Column Names

The current version of `grDevices::convertColor` produces seemingly odd column
names.  For example, in this case one might expect both results to have the same
column names:

```{r}
convertColor(c(50, -20, 20), 'Luv', 'Lab')
convertColor(c(.34491, .50319, .37791), 'sRGB', 'Lab')
```

These seemingly odd names are likely an unintended consequence of `c` combining
the names of inputs:

```{r}
c(L=50, a=-20, b=13)
c(L=c(Y=50), a=c(X=-20), b=c(Y=13))
```

Internally we replace calls to `c` with `cbind`, and this "resolves" the issue.
It would be possible to record the old names for each combination of inputs and
reproduce them, but this requires contortion for the sake of behavior that does
not seem worth preserving.

## Zero Row Inputs

Almost all color space conversions currently fail with zero row inputs, except
those in which `to` is set to `XYZ`.  For these the  return is a zero length
vector.  With the patch all input/output color space combinations work and
return zero-row matrices:

```{r}
convertColor(matrix(numeric(), ncol=3), 'Luv', 'XYZ')
convertColor(matrix(numeric(), ncol=3), 'Luv', 'Lab')
str(grDevices1::convertColor(matrix(numeric(), ncol=3), 'Luv', 'XYZ'))
str(grDevices1::convertColor(matrix(numeric(), ncol=3), 'Luv', 'Lab'))
```

Given that this is a bit of a corner case, and that the existing behavior is
inconsistent across input/output color space combinations, it seems unnecessary
to further complicate the patches to mimic the existing behavior.

## NAs/NaNs/Inf in Inputs

NA/NaN/Inf inputs currently cause errors for many of the input/output color
space  combinations.  This is mostly because of expressions of the form
`if(test) ...` fail when `test` is NA, as shown in this example:

```{r}
convertColor(c(NaN, 0.5, 0.5), 'sRGB', 'Lab')   # works
convertColor(c(NaN, 0.5, 0.5), 'Lab', 'sRGB')   # doesn't
```

The level-1 patch uses `ifelse` which handles the NA values and propagates
them. In this sense level-1 "works".  The level-2 patch replaces `ifelse` with
the faster `.ifelse`, which works similarly but also preserves NaNs (i.e. does
not coerce them to NAs):

```{r}
grDevices1::convertColor(c(50, NaN, 0.5), 'Lab', 'sRGB')
grDevices2::convertColor(c(50, NaN, 0.5), 'Lab', 'sRGB')
```

Due to the existing inconsistency, there seems to be little harm in changing the
behavior to make NAs propagate and allow the computation to complete.
